\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2021-04-09 sections/methods.tex
Add: Subsection for the consensus method

>>>>

  \subsection{Consensus method}
  \vspace{-5mm}

  The consensus algorithm was designed to increase the number of true positives reported at the end of the network inference step. For this purpose, we designed two simple algorithms that combine the edges reported by the different network inference tools for each pair of nodes using a consensus based on a parameter \(p\). The inputs to both the algorithms are the interaction networks (association matrices) generated by each method \(N_{i}\) and the threshold parameter \(p\). Here, the \(N_{i}\) each have the same set of nodes and only differ by the value of the association inferred between every pair.

  \subsection{Algorithm 1: Simple voting}
  \label{sec:org34a8cdc}

  The simple voting method performs a voting-based consensus to determine whether an edge will exist between a given node-pair in the final consensus network. For each pair of nodes \((\text{node}_{i}, \text{node}_{j})\), we determine the number of network inference methods that report an edge between them (\(\text{edges}(\text{node}_{i}, \text{node}_{j})\)). Each node-pair will have an edge in the final consensus network if the number of reported edges is more than a threshold (Equation \ref{eqn:simple-voting})

  \begin{equation}
  \text{edges}(\text{node}_{i}, \text{node}_{j}) \geq \lfloor p * x \rfloor
  \label{eqn:simple-voting}
  \end{equation}
  where, \(x\) is the number of network inference methods used in the consensus.

  The simple voting method gives the union of the networks when \(p \in (0, \frac{1}{x})\) and will return the intersection when \(p \in ((x - 1), 1)\). In general, if \(p \in ((n - 1), \frac{n}{x})\), this algorithm will report an edge in the consensus network when at least \(n\) network inference methods report this edge.

  \subsection{Algorithm 2: Scaled-sum method}
  \label{sec:orgb0ddb1f}

  This algorithm performs a consensus based on sum of all edges reported between a node-pair. First, the network generated by each network inference method is re-scaled so that \(\max(\mid N_{i} \mid) = 1\) (Equation \ref{eqn:scaled-sum-rescaling}).

  \begin{equation}
  N^{scaled}_{i} = \frac{N_{i}}{\max(\mid N_{i} \mid)}
  \label{eqn:scaled-sum-rescaling}
  \end{equation}

  The re-scaling is performed because the associations reported by the direct association metrics are not necessarily correlations and are not directly comparable to the associations from the correlation-based methods due to their lower weights. This problem can also be alleviated by weighing each network inference method differently. Next, for each pair of nodes, we sum the weights of all reported edges (Equation \ref{eqn:scaled-sum})

  \begin{equation}
  \text{scaled\_sum}(\text{node}_{m}, \text{node}_{n}) = \sum_{i} N^{scaled}_{i}(\text{node}_{m}, \text{node}_{n})
  \label{eqn:scaled-sum}
  \end{equation}

  An edge will exist between a given node-pair in the consensus network if \(\text{scaled\_sum} > (x - 1) * p\), where \(x\) is the number of network inference methods used in the consensus. The advantage of this method is that it also takes into account how the strength of the association reported for that particular node is in the inferred networks.
